%!TEX root = ../MCGT_Thesis.tex

% \begin{savequote}[8cm]
% \textlatin{Neque porro quisquam est qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit...}

% There is no one who loves pain itself, who seeks after it and wants to have it, simply because it is pain...
% % \qauthor{--- Cicero's \textit{de Finibus Bonorum et Malorum}}
% \end{savequote}

% \minitoc


\chapter*{Introduction}
\label{ch:0-intro}
% [This paragraph need rewriting/revising from HERE] \\

%  One in five of all Europeans suffer from chronic pain. This specific clinical condition occurs when pain is experienced over a period that lasted longer than three to six months and certainly beyond any expected period of healing. Chronic pain can limit the ability to live a meaningful and satisfying daily life, and current research suggests that half of the patients suffering with chronic pain are not receiving adequate treatment to improve their experience of pain or their general functioning. Pain limits what one want to or can do, and many patients have in fact a narrow focus on their pain. This narrow focusing,  poses significant limits and in their general and daily functioning and lower job productivity/potential which both have an obvious impact on our society in terms of health care and societal cost. It is estimateD that inadequate coping may lead to continuation of the pain and subsequently lead to higher health costs and lower productivity at their job \parencite{severeijns2001pain}. Persistence pain has in fact huge society costs: in the UK, back pain alone is estimated to cost society £17–32 billion each year \parencite{maniadakis2000economic}, while in the US \textcite{turk2011treatment} reports that the overall societal cost of chronic pain is £140 billion per year.

% [TO HERE]

\section*{Contribution}


Phasellus dis Tristique iaculis sagittis ut fusce facilisi libero. Ullamcorper nonummy feugiat felis, sagittis viverra hymenaeos conubia arcu. Nonummy potenti tempor nunc massa penatibus pulvinar odio nisi hac eleifend, euismod. Erat eleifend odio dignissim aliquet. Tortor luctus tellus, sit. Ultrices luctus. Fringilla habitasse ultrices porttitor. Auctor, vulputate. Bibendum habitasse cubilia nisl mi magna in dolor. Sollicitudin morbi nulla nostra fames felis sed sed per Sociosqu cubilia molestie. Sapien consequat nec cum. Blandit curae;. Platea a volutpat erat conubia nibh mauris fringilla Convallis, metus dictum dolor dis lobortis sociosqu. Torquent dictumst conubia phasellus bibendum. Gravida. Maecenas sagittis nullam tellus semper nullam ridiculus Morbi inceptos lobortis nam laoreet id ridiculus sit arcu. Litora. Faucibus urna facilisis ipsum. Rhoncus mauris congue eros lectus tempor cursus conubia dis suspendisse montes nascetur venenatis litora tortor sed a auctor senectus natoque consectetuer lacinia gravida sem mauris ipsum donec penatibus. Lacinia class pellentesque imperdiet justo interdum in, nam lacinia. Sociis. Malesuada lacinia habitant conubia penatibus Nisi hendrerit nascetur sociis montes. Sem ultricies eu aenean egestas, congue accumsan Platea penatibus dapibus. Auctor, blandit semper phasellus sit facilisi morbi potenti pulvinar iaculis ipsum penatibus adipiscing suspendisse dis fringilla malesuada interdum dolor, lacinia sodales mattis sodales nonummy ad scelerisque Litora fermentum. Facilisi commodo interdum maecenas. Nonummy porttitor aliquam dui sed. Dis. Fames leo pellentesque quam hac semper. Lacinia.

[TO HERE]
